Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-15 manuscript/manuscript.tex
small tweaks

\begin{figure}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/simulations}}
\caption{\label{fig:simulations}
\textbf{Model performance under simulated, site-specific data.} 
Alignments were simulated under an ExpCM and branch lengths were re-estimated using models from the ExpCM and GY94 families. 
The averaged ExpCMs have a uniform stationary state defined by the average preference for each amino acid across all sites in the protein. 
The length of one branch in one simulation is shown in grey and the average branch length of one branch across ten simulations is shown in black. 
The grey, dashed line is the reference line $y=x$, representing the behavior of an unbiased estimator. 
}
\end{figure}

@@

Models with either site-specific stationary state or $\Gamma\omega$ rate variation estimated longer branches than models without (\ref{fig:empirical_trees}). 
Furthermore, we can isolate the effect of each method to account for purifying selection from the other. 
For example, the increase in branch length estimated by GY94+$\Gamma\omega$ compared to GY94 and by ExpCM+$\Gamma\omega$ compared to ExpCM shows that $\Gamma\omega$ rate variation increases branch length in the presence and absence of a site-specific stationary state. 
We also see an increase in branch length with the addition of a site-specific stationary state in the presence and absence of $\Gamma\omega$ rate variation (\ref{fig:empirical_trees}, GY94 vs. ExpCM and GY94+$\Gamma\omega$ vs. ExpCM+$\Gamma\omega$). 
The model with both methods, ExpCM+$\Gamma\omega$, estimated the longest branches of all the models. 
However, the branch length extension from any of the ExpCM compared to any of the GY94 models was not uniform across the entire tree. 
The branches with the largest difference in branch length are near the focal sequence of the deep mutational scans (\ref{fig:empirical_trees}, circle for H1 and triangle for H3)
This local effect of the ExpCM indicates that the stationary state described by the deep mutational scanning preferences is most accurate near the focal sequences of the scan.

>>>>

\begin{figure}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/simulations}}
\caption{\label{fig:simulations}
\textbf{Model performance under simulated, site-specific data.} 
Alignments were simulated under an ExpCM and branch lengths were re-estimated using models from the ExpCM and GY94 families. 
The averaged ExpCMs have a uniform stationary state defined by the average preference for each amino acid across all sites in the protein. 
The length of one branch in one simulation is shown in grey and the average length of one branch across ten simulations is shown in black. 
The grey, dashed reference line $y=x$ represents the behavior of an unbiased estimator. 
}
\end{figure}

@@

Models with either site-specific stationary state or $\Gamma\omega$ rate variation estimated longer branches than models without (\ref{fig:empirical_trees}). 
Furthermore, we can isolate the effect of each method. 
For example, the increase in branch length estimated by GY94+$\Gamma\omega$ compared to GY94 and by ExpCM+$\Gamma\omega$ compared to ExpCM shows that $\Gamma\omega$ rate variation increases branch length in the presence and absence of a site-specific stationary state. 
We also see an increase in branch length with the addition of a site-specific stationary state in the presence and absence of $\Gamma\omega$ rate variation (\ref{fig:empirical_trees}, GY94 vs. ExpCM and GY94+$\Gamma\omega$ vs. ExpCM+$\Gamma\omega$). 
The model with both methods, ExpCM+$\Gamma\omega$, estimated the longest branches of all the models. 
However, the branch length extension from any of the ExpCM compared to any of the GY94 models was not uniform across the entire tree. 
The branches with the largest difference in branch length are near the focal sequence of the deep mutational scans (\ref{fig:empirical_trees}, circle for H1 and triangle for H3)
This local effect of the ExpCM indicates that the stationary state described by the deep mutational scanning preferences is most accurate near the focal sequences of the scan.
